Painting with Triangles

### 2014-04-21 paper.tex
Changed figures
foo

Another line of research has explored entirely new ways of painting.
Orzan~\etal~\shortcite{Orzan:2008:DCV:1360612.1360691}
specified Diffusion curves which
describe a new painting technique where artists specify edges and colors for those edges. Their system
then solves a Poisson equation to diffuse the colors between boundary conditions specified at the edges.
Similarly the method of McCann and Pollard~\shortcite{McCann:2008:RGP:1360612.1360692}
lets artists paint in the gradient domain. Both of these approaches yield creative new aesthetic ranges 
beyond what is straightforward in the traditional pixel-based painting model. Nevertheless,
they represent a new painting metaphor for the artist, rather than a vectorized version of the conventional
digital painting approach familiar to artists.

@@

\begin{figure}
    \centering
        \includegraphics[width=0.4\textwidth]{images/colorarcsfinal}
    \caption{An example of color arcs. The orange lines are boundary edges. Black lines form the triangle
    mesh with the boundary edges. Each point is given a color arc which defines its color in that range.
    Note that the points in the middle row have different colors on top and bottom. This gives blue
    triangles on top and red on bottom with a hard boundary in between.}
    \label{fig:arcs}
\end{figure}

@@

\subsection{Converting Contours to Triangles}
The contour contains two important pieces of information. First, it describes all of the points of the stroke.
Second, segments connecting adjacent points describe the boundaries of the stroke. 
A triangle mesh must contain all the points and stay
within the boundaries. For example, a concave contour should not contain triangles inside the concavity since such triangles
would be outside of the boundary.
Furthermore, these boundaries will later be crucial when compositing a stroke onto a canvas.

We utilized Jonathan Shewchuk's Triangle library~\cite{shewchuk2002} to perform constrained Delaunay triangulations
on the given set of points and boundaries. The library outputs a mesh that
approximately represents the drawn stroke.

@@

\subsection{Soft Strokes}
The above procedure converts a hard brush stroke into a triangle mesh. A more interesting
case is converting a soft brush stroke with linear gradient into a triangle mesh. A soft stroke has two
components, an inner hard stroke and an outer gradient stroke. Since the triangles in the inner and
outer parts of the stroke must be colored differently, none of the triangles may cross the boundary
between the hard and soft regions.

>>>>

Another line of research has explored entirely new ways of painting.
Orzan~\etal~\shortcite{Orzan:2008:DCV:1360612.1360691}
introduced \emph{diffusion curves} --
a new painting technique where artists specify edges and colors for those edges. Their system
then solves a Poisson equation to diffuse the colors between boundary conditions specified at the edges.
Similarly the method of McCann and Pollard~\shortcite{McCann:2008:RGP:1360612.1360692}
lets artists paint in the gradient domain. Both of these approaches yield creative new aesthetic ranges 
beyond what is straightforward in the traditional pixel-based painting model. Nevertheless,
they represent a new painting metaphor for the artist, rather than a vectorized version of the conventional
digital painting approach familiar to artists.

@@

\begin{figure}
    \centering
        \includegraphics[width=0.4\textwidth]{images/colorarcsfinal}
    \caption{Color arcs. Orange lines are boundary edges, and together with black lines form the triangle
    mesh. Each point is given more or more color arcs, 
    which stores the color of triangle corners in that angular range.
    Points in the middle row have red arcs on top and blue below,
    yielding triangles with those colors, separated by a hard boundary.}
    \label{fig:arcs}
\end{figure}

@@

\subsection{Converting Contours to Triangles}
The contour contains two important pieces of information. First, it describes all of the points of the stroke.
Second, segments connecting adjacent points describe the boundaries of the stroke. 
A triangle mesh must contain all the points and stay
within the boundaries. 
For example, a concave contour like the outline of the letter C should not contain 
triangles inside the concavity, since such triangles would be outside of the boundary.
These boundaries will prove to be crucial when compositing a stroke onto the canvas.
%
We perform constrained Delaunay triangulation on the given set of points and boundaries using
Shewchuk's implementation~\shortcite{shewchuk2002}, and the output is a mesh that
approximately represents the drawn stroke.

@@

\subsection{Soft Strokes}
The above procedure converts a hard brush stroke into a triangle mesh. A more challenging
case is converting a soft brush stroke with linear gradient into a triangle mesh. A soft stroke has two
components, an inner hard stroke and an outer gradient stroke. Since the triangles in the inner and
outer parts of the stroke must be colored differently, none of the triangles may cross the boundary
between the hard and soft regions.
